---
title: "Description for HW4"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)
library(p8105.datasets)
library(plotly)


knitr::opts_chunk$set(
 	echo = TRUE,
 	warning = FALSE,
 	fig.width = 8, 
   fig.height = 6,
   out.width = "90%"
 )

options(
   ggplot2.continuous.colour = "viridis",
   ggplot2.continuous.fill = "viridis"
 )

 scale_colour_discrete = scale_colour_viridis_d
 scale_fill_discrete = scale_fill_viridis_d

 theme_set(theme_minimal() + theme(legend.position = "bottom"))
```


```{r, dataset}
data("rest_inspec")

rest_inspec =
  rest_inspec %>%
  filter(grade %in% c("A", "B", "C", "Not Yet Graded"), boro != "Missing") %>% 
  mutate(boro = str_to_title(boro))
```

# Description

Dataset is not tidy, it contains multiple observations for the same restaurant, it does not contain identification number for each inspection and for each place or long and lan, which makes it impossible to deferentiate among chain restaurants if they are locate on the same street. Storing this information in the relational database would provide clarity and simplicity of analysis.

```{r, plot 1}
grade_over_t = 
  rest_inspec %>% 
  group_by(grade) %>% 
  filter(
    str_detect(dba, regex("tequil", ignore_case = TRUE))) %>% 
  ggplot(aes(x = inspection_date, y = grade, color = dba, group = dba))+
  geom_point() + geom_line() +
  labs (
    title = "Grades Over Time For Tequila Bars",
    x = "Year",
    y = "Grade",
    caption = "Data from nyc.gov"
  )

ggplotly(grade_over_t)
```

``` {r, plot 2}
density = 
  rest_inspec %>% 
  filter(str_detect(cuisine_description, regex ("kosher", ignore_case = TRUE))) %>% 
  ggplot(aes(x = boro, fill = grade)) +
  geom_density(alpha = .5) +
  labs (
    title = "Distribution Of Grades For Kosher Restaurants Among Boros ",
    x = "Boro",
    y = "Density",
    caption = "Data from nyc.gov"
  )

ggplotly(density)
```

```{r, plot 3}
rest_inspec %>% 
  group_by(cuisine_description, boro) %>% 
  count(cuisine_description, sort = TRUE) %>% 
  plot_ly(x = ~ cuisine_description, y = ~n, color = ~ boro, type = "bar") %>% 
    layout(
    title = "Total Count Of Top 15 Most Popular Cuisines By Boro")
```


